New seismological constraints on the available parameter space of macroscopic dark matter

### 2016-09-07 LaTeX/Article_Draft.tex
A few more style things
.

\subsection{Heat Equation solution analysis}
We consider only the melting or vaporization that occurs prior to the onset of the deposited energy serving as a source for seismic waves, since the initiation of seismic wave propagation complicates assessing the amount of energy dissipated in melting (and vaporizing) the impacted material and its surroundings.  To model an instantaneous energy deposition along the z-axis, we use a delta function, and set the solution of the heat equation equal to a fixed temperature (of melting).  This yields an expression for the radius, as a function of time, of the impacted material and its surroundings that has reached its melting point temperature, $r_\te{melt}(t)$.  Differentiating $r_\te{melt}(t)$ with respect to time, setting the result equal to the bulk speed of sound and solving for t yields the time at which the propagation of the "melt point temperature zone" falls to the speed of sound.  Plugging this time into $r_\te{melt}(t)$ yields $r_\te{fast melt}$: the extent of the impacted material and its surroundings that is heated to its melting point more rapidly than bulk sound speed. Replacing the melting point temperature with the vaporization point temperature in the above demonstrates that $r_\te{fast melt}$ is essentially equal to $r_\te{fast vaporize}$ for all Macro radii.  This result indicates that for macros with radii greater than ***$10^{-9} m$***(pending resolution of consistency check issue, and minor additional refinements), $r_\te{fast vaporize}$ is of the same order as $r_\te{Macro}$.
The extreme temperatures generated by the impact (approximately $10^{15} K$, again pending resolution of consistency check issue that arose in computing this value) will convert the vaporized material to plasma; however, this conversion is a second order phase transition, and so does not require a latent heat input to occur.  Thus, the energy to transition from vapor to plasma could conceivably transfer back into seismic waves (as the particles slow down, recombine as vapor, condense to liquid, and then solidify). Similarly, the energy required to raise the temperature of the impacted material and its surroundings to their melting and vaporization points could subsequently source seismic waves: temperature changes in the column of heated material result in expansions  and contractions that lead to a column of ovepressure/underpressure. Hence, to model the energy dissipated both in raising the temperature of the impacted material and its surroundings, and in effecting a transition to plasma are complicated by the concurrent energy transfer to seismic waves.

>>>>

\subsection{Heat Equation solution analysis}
We consider only the melting or vaporization that occurs prior to the onset of the deposited energy serving as a source for seismic waves, since the initiation of seismic wave propagation complicates assessing the amount of energy dissipated in melting (and vaporizing) the impacted material and its surroundings.  To model an instantaneous energy deposition along the z-axis, we use a delta function, and set the solution of the heat equation equal to a fixed temperature (of melting). This yields an expression for the radius, as a function of time, of the impacted material and its surroundings that has reached its melting point temperature, $r_\te{melt}(t)$.  Differentiating $r_\te{melt}(t)$ with respect to time, setting the result equal to the bulk speed of sound and solving for t yields the time at which the propagation of the "melt point temperature zone" falls to the speed of sound.  Plugging this time into $r_\te{melt}(t)$ yields $r_\te{fast melt}$: the extent of the impacted material and its surroundings that is heated to its melting point more rapidly than bulk sound speed. Replacing the melting point temperature with the vaporization point temperature in the above demonstrates that $r_\te{fast melt}$ is essentially equal to $r_\te{fast vaporize}$ for all Macro radii.  This result indicates that for macros with radii greater than ***$10^{-9} m$***(pending resolution of consistency check issue, and minor additional refinements), $r_\te{fast vaporize}$ is of the same order as $r_\te{Macro}$.  A simple computation shows that the heat dissipated in sublimating a column of material with radius $r_\te{fast vaporize}$ ranges from less than $1 J$ to $10^2 J$, a negligible amount (note, these details are all found in Macro impacts revised eqs. 306-322). 
The extreme temperatures generated by the impact (approximately $10^{15} K$, again pending resolution of consistency check issue that arose in computing this value) will convert the vaporized material to plasma; however, this conversion is a second order phase transition, and so does not require a latent heat input to occur.  Thus, the energy to transition from vapor to plasma could conceivably transfer back into seismic waves (as the particles slow down, recombine as vapor, condense to liquid, and then solidify). Similarly, the energy required to raise the temperature of the impacted material and its surroundings to their melting and vaporization points could subsequently source seismic waves: temperature changes in the column of heated material result in expansions  and contractions that lead to a column of ovepressure/underpressure. Hence, to model the energy dissipated both in raising the temperature of the impacted material and its surroundings, and in effecting a transition to plasma are complicated by the concurrent energy transfer to seismic waves.
The force of these results are that either much of the melting occurs once the temperature field's expansion is slower than the speed of sound and this slow-down occurs very quickly, or that the material parameters -- especially the thermal diffusion coefficient and the heat capacity of the impacted material -- are far from constant in the case at hand (given the extremes of pressure and temperature involved, it is more likely the latter).  In addition, the instantaneous energy deposition model de-emphasizes the significance of the parameters of the macro, and appears to (over)emphasize the significance of the parameters of the impacted material.
